---
title: "Body Mass Tracker"
subtitle: "In the summer I will be a skinny snowman"
author: "Terrel Shumway"
date: "04/13/2015"
output: html_document
---
On March 22, our company started a "health challenge".  It is not quite a biggest loser contest, but more of a "How can you become healthier than you are?"  Well, for me, the obvious low-hanging fruit is losing my flab. I started at 203 pounds with a BMI of 31. Yuck.

```{r, echo=FALSE}
origin = as.POSIXct(strptime("1970-01-01 00:00:00", "%Y-%m-%d %H:%M:%S"))
height = 68
bmi = function(mass){mass/(height*height)*705}

BM = data.frame(date=strptime(
  c("2015/3/22","2015/4/7","2015/4/8","2015/4/10","2015/4/11","2015/4/12",
    "2015/4/13"
    ),
  "%Y/%m/%d"
  ),mass=c(203,198.6,197.6,198.2,197.8,193.6,
           193.8           
    ))

baseline = BM[1,"mass"]

BM$BMI = bmi(BM$mass)

```

This chart will track my progress:

```{r,echo=FALSE}
m1 = lm(mass~date,data=BM)
plot(BM$date,BM$mass,xlab="Date",ylab="mass (pounds)",main="Body Mass Over Time")
abline(m1)
BM
```

```{r}
m2 = lm(date~mass,data=BM)
targets = data.frame(mass=baseline*c(.95,.9,.85,.8,.75))
targets$date= as.POSIXct(predict(m2,targets),origin=origin)
targets$BMI = bmi(targets$mass)
targets
```

A simple linear regression model predicts that I will reach 80% of my baseline on `r strftime(targets[4,"date"],"%m/%d")` (Julie thinks that 150 lbs. is too skinny, so I *may* stop there.) 

See also the [CDC site on obesity](http://www.cdc.gov/obesity/adult/defining.html).
